Papers_search_solutions

### 2019-02-07 R/Papers_search_solutions.Rmd
added some bold and italic formatting, line breaks

**ANSWER 11:**   
It depends on the effect size we are planning to use. In our project it can be Cohen's d (Hedges g) or lnRR, which are typically calculated from mean, SD or SE and N (sample sizes). However, Cohen's d (Hedges g) can be also inferred from some of the test statistics, or even proportions, if means and other descriptive statistics are not available. But one cannot get lnRR from inhferential statistics. Other considerations include what to do if some data is missing or unclear.

@@

**ANSWER 16:**   
We think 4 should have been excluded: Simmons2009 and Clancy2013 as human studies, Gershman2010 and Gonzales-Tokman2013 as not likely to have any reproduction-related measurements.

**ANSWER 17:**    
Nielsen2012 - include, Ardia2005 - exclude due to the lack of good control group.

>>>>

**ANSWER 11:**   
It depends on the effect size we are planning to use. In our project it can be Cohen's *d* (Hedges *g*) or *lnRR*, which are typically calculated from mean, SD or SE and N (sample sizes). However, Cohen's *d* (Hedges *g*) can be also inferred from some of the test statistics, or even proportions, if means and other descriptive statistics are not available. But one cannot get *lnRR* from inhferential statistics. Other considerations include what to do if some data is missing or unclear.

@@

**ANSWER 16:**   
We think 4 should have been excluded:    
**Simmons2009** and **Clancy2013** as human studies, but    
**Gershman2010** and **Gonzales-Tokman2013** as not likely to have any reproduction-related measurements.

**ANSWER 17:**    
**Nielsen2012** - include, **Ardia2005** - exclude due to the lack of good control group.
